The Etiology of Cybersecurity

### 2020-07-23 reports/paper_0/main.tex
sec 4b minor review

Based on these hypothesis, we can formulate the concepts of security and
insecurity (in the $\abftheory$-framework) as mathematical equations.  Let us consider a CPS
$S$, represented as a graph $G=\langle V,E\rangle$ where $V$ represents the
set of functional blocks and ports of $S$, and $E\subseteq V\times E$ is the
set of pairs representing the channels and connections (data flows) between
functional blocks. We define $R\subseteq V\times F$, where $F$ is the set
of all the requirements of $S$, and extend $G$ as $G'=\langle E'\times V'\rangle$
with $E'= E\cup R$ and $V'=V\cup F$. Let $\pi: E'\rightarrow RCC$ (where $RCC$ is
the set of relations in the RCC) be
the total function associating an RCC relation to each edge in $G'$, and
$\Pi$ be the set of all different permutations of RCC relations over $E'$
(i.e. $\Pi=\{\langle\pi(e_0)=EQ,\ldots,\pi(e_n)=EQ\rangle,\ldots,\langle \pi(e_0)=DR,\ldots,\pi(e_n)=DR\rangle\}$). If $\sigma:\Pi\rightarrow\{0,1\}$ is an evaluation function
such that $\sigma(p)=1$ (where $p\in\Pi$) iff the input configuration is satisfiable with respect to
the logical theory defining the algebraic structure (mereotopology) and constraints
of the calculus RCC (otherwise $\sigma$ returns $0$), we can define
\begin{displaymath}
	I=\sum_{p\in\{\Pi\setminus\pi_{eq}\}} \sigma(p)
\end{displaymath}
where $\pi_{eq}\in\Pi$ is the output of the function $\pi$ that associates only EQ relations
to any $e\in E'$, and $I\in\mathbb{N}$ represents all the insecurity configurations
of the CPS $S$ where, at least, one of the RCC relations isn't EQ.
In other words, we consider $\pi_{eq}$ as the only secure configuration.

@@

\subsection{Security Risk Assessment}\label{sec:secra}
In order to test our theory we implemented a tool-chain (open-source under the
AGPLv3 license and available at \autocite{v-research2020cybersecurity}) for the
identification of weaknesses and the precise calculation of potential insecure
configurations. The engineering of the $\abftheory$ is summarized in the UML
Class diagram in Figure~\ref{fig:secraclassdiagram} (in appendix).

>>>>

Based on these hypothesis, we can formulate the concepts of security and
insecurity (in the $\abftheory$-framework) as mathematical equations.  Let us
consider a CPS $S$, represented as a graph $G=\langle V,E\rangle$ where $V$
represents the set of functional blocks and ports of $S$, and $E\subseteq
V\times E$ is the set of pairs representing the channels and connections (data
flows) between functional blocks. We define $R\subseteq V\times F$, where $F$
is the set of all the requirements of $S$, and extend $G$ as $G'=\langle
E'\times V'\rangle$ with $E'= E\cup R$ and $V'=V\cup F$. Let $\pi:
E'\rightarrow RCC$ (where $RCC$ is the set of relations in the RCC) be the
total function associating an RCC relation to each edge in $G'$, and $\Pi$ be
the set of all different permutations of RCC relations over $E'$ (i.e.
$\Pi=\{\langle\pi(e_0)=EQ,\ldots,\pi(e_n)=EQ\rangle,\ldots,\langle
\pi(e_0)=DR,\ldots,\pi(e_n)=DR\rangle\}$ where $e_i\in E'$ for $0\leq i \leq n$ and $|E'|=n$). If $\sigma:\Pi\rightarrow\{0,1\}$ is
an evaluation function such that $\sigma(p)=1$ (where $p\in\Pi$) iff the input
configuration is satisfiable with respect to the logical theory defining the
algebraic structure (mereotopology) and constraints of the calculus RCC
(otherwise $\sigma$ returns $0$), we can define
\begin{displaymath}
	I=\sum_{p\in\{\Pi\setminus\pi_{eq}\}} \sigma(p)
\end{displaymath}
where $\pi_{eq}\in\Pi$ is the output of the function $\pi$ that associates only EQ relations
to any $e\in E'$, and $I\in\mathbb{N}$ represents all the insecurity configurations
of the CPS $S$ where, at least, one of the RCC relations isn't EQ.
In other words, we consider $\pi_{eq}$ as the only secure configuration.

@@

\subsection{Cybersecurity Risk Assessment}\label{sec:secra}
In order to test our theory we implemented a tool-chain (open-source under the
AGPLv3 license and available at \autocite{v-research2020cybersecurity}) for the
identification of weaknesses and the precise calculation of potential insecure
configurations. The engineering of the $\abftheory$ is summarized in the UML
Class diagram in Figure~\ref{fig:secraclassdiagram} (in appendix).
